Analysis of Massachusetts Standardized Testing Data through Structural Equation Modelling

### 2014-03-13 paper.Rnw
Notes on direction for paper

\section*{Discussion}
Could also include ideas for other questions to ask in the questionairre

>>>>

- Questionairre results - regression tree

Results from "omega" exploratory data analysis
- diagram of factor loadings

Model Structure

Table
- Results from factor invariance

\section*{Discussion}
Test doesn't work the same across races

Could be because of SES?

Questionairre results

Could also include ideas for other questions to ask in the questionairre
